A Comparison of Parallel Graph Processing Implementations

### 2017-05-15 papers/publication/paper-pollard.tex
added power to future

Listing~\ref{lst:RAPL} shows the simplicity of adding RAPL profiling to existing code. Once the source code is modified, the implementation may be recompiled and our provided header file linked in. Alternatively, there may be scenarios where this approach is not feasible. For example, in some cases, if the user does not have root privileges s/he may not be able to access the model specific registers storing the energy usage. One alternative is to use TAU paired with PAPI to instrument the source code, and if the counters are available on the host CPU then the power and energy can still be measured.

@@

>>>>

Listing~\ref{lst:RAPL} shows the simplicity of adding RAPL profiling to existing code. Once the source code is modified, it is compiled with our provided header file and linked with a small library. Alternatively, there may be scenarios where this approach is not feasible. For example, in some cases, if the user does not have root privileges s/he may not be able to access the model specific registers storing the energy usage. One alternative is to use TAU paired with PAPI to instrument the source code, and if the counters are available on the host CPU then the power and energy can still be measured.

@@

With respect to power and energy profiling, while our current implementation supports measurements based on PAPI's interface to RAPL, which is only available on Intel platforms, the interface is simple and easy to adapt to other platforms in future without requiring PAPI support. In particular, fine-grained measurements provided through potentially available custom hardware~\cite{naecon15} can be enabled through the same interface.
